Measurement and Probability in Fuzzy Quantum Theories

### 2017-04-28 prop_iop.tex
prop_iop.tex \section{Expectation Values for IVPMs} Updating...

\begin{lemma}\label{lemma:QIVPM2QCM}Let $\mathscr{I}_{\mathrm{D}}$
be $\left\{ \imposs,\necess\right\} $. Given a quantum interval-valued
probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
$\mu:\events\rightarrow\left[0,1\right]$ defined by 
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
1 & if $\bar{\mu}(P)=\necess$ ,
}\end{equation}
 is a cryptodeterministic measure.\end{lemma}

@@

@@

Our next lemma discusses the Choquet integral on the real-valued probability
measure reduced to the conventional expectation value.

>>>>

\begin{lemma}\label{lemma:QIVPM2QCM}Let $\mathscr{I}_{\mathrm{D}}$
be $\left\{ \imposs,\necess\right\} $. Given a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
then $\mu:\events\rightarrow\left[0,1\right]$ defined by 
\begin{equation} 
\mu(P)=\cases{ 
0 & if $\bar{\mu}(P)=\imposs$ ;\\ 
1 & if $\bar{\mu}(P)=\necess$
}\end{equation}
is a cryptodeterministic measure.\end{lemma}

@@

\begin{lemma}\label{lemma:Choquet-Lebesgue}\cite{Grabisch2016}When
$\mul:\events\rightarrow\left[0,1\right]$ and $\mur:\events\rightarrow\left[0,1\right]$
are real-valued probability measures, we have $\mul=\mur$ and $\int X\rmd\bar{\mu}=\left\{ \int X\rmd\mul\right\} =\left\{ \int X\rmd\mur\right\} $.\end{lemma}

@@

Our next lemma discusses the quantum version of lemma~\ref{lemma:Choquet-Lebesgue}.

\begin{lemma}Given a Hilbert space of $d\ge3$, when $\mul:\events\rightarrow\left[0,1\right]$
and $\mur:\events\rightarrow\left[0,1\right]$ are real-valued probability
measures, we have $\mul=\mur=\mu_{\rho}^{\mathrm{B}}$ for some density
matrix~$\rho$. Then, $\expval{\mathbf{O}}_{\bar{\mu}}=\left\{ \expval{\mathbf{O}}_{\rho}\right\} $.\end{lemma}

\begin{proof}The first part of the lemma is the consequence of Gleason's
theorem directly. For the second part of the lemma \end{proof}
